---
title: "Nothing"
subtitle: "Author: Me"
output:
  ioslides_presentation:
    css:
      rslides.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Words

The logo graphic will be rescaled <http://outlook.com> to 85x85 (if necessary) and added to the title slide. A smaller icon version of the logo will be included in the bottom-left footer of each slide.

The logo on the title page and the rectangular element containing it can be customised with CSS. For example

## Bullet stuff

- words
- more words
- even more words

## R stuff

```{r cars, echo = TRUE}
summary(cars)
```

## Graph that is actually an image

```{r pressure}
plot(pressure)
```

## Table things

ID    Fruit        Color
----- ---------- ---------
1     Apple      red
2     Pear       green
4     Watermelon green
7     Grapes     red/green
9     Banana     yellow
10    Mango      yellow
11    Pineapple  yellow
14    Cherry     red
15    Strawberry red
17    Blueberry  blue
